|

### 2021-03-16 appendix/appendix.Rmd
multilevel reg forest plot

# Build plot function for forest plots
build_forest <- function(mod, capt, lsize = 22, ttl = NULL) {
  # Build dataset for plot
  mod2 <- tibble(
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    bind_rows(.,
              aux = tibble(
                TE = c(mod$TE.random, NA),
                seTE = c(mod$seTE.random, NA),
                studlab = c("Overall Effect",
                            "Prediction Interval"),
                lower = c(mod$lower.random,
                          mod$lower.predict),
                upper = c(mod$upper.random,
                          mod$upper.predict),
                group = "B")) %>%
    group_by(studlab) %>%
    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
    ungroup()

@@

In this paper, we use the random effects model. The empirical papers testing the *law of 1/n* are very diverse. We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:

@@

In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in [Doing Meta-Analysis with R](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html). To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$. We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it the most precise when analysing continuous measures, such as we have in our data (XXXX TO UMBERTO: PUT CITATION HERE).

@@

# Code for the Main Graphs

## Figure 1

```{r, echo=T, warning=F, cache=TRUE, echo = FALSE}
pdf('../graphs/graph1.pdf', width = 16, height = 11)
ggarrange(f1,f3,f5,f4,f6,f2,f7, align = 'hv')
dev.off()
```

## Figure 2

```{r, echo=T, warning=F, cache=TRUE, echo = FALSE}
pdf('../graphs/graph2.pdf', width = 12, height = 6)
ggarrange(f8, f9, align = 'hv')
dev.off()
```

>>>>

# Broom the multi-level model
broom_mod <- function(mod) {
  aux <- data.frame(predict(mod))
  mod2 <- tibble(
    TE = as.numeric(mod$yi),
    seTE = sqrt(mod$vi),
    studlab = mod$slab,
    lower = as.numeric(mod$yi)-1.96*sqrt(mod$vi),
    upper = as.numeric(mod$yi)+1.96*sqrt(mod$vi),
    group = 'A') %>%
    bind_rows(.,
              aux = tibble(
                TE = c(aux$pred, NA),
                seTE = c(aux$se, NA),
                studlab = c("Overall Effect",
                            "Prediction Interval"),
                lower = c(aux$ci.lb,
                          aux$cr.lb),
                upper = c(aux$ci.ub,
                          aux$cr.ub),
                group = "B")) %>%
    group_by(studlab) %>%
    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
    ungroup()
  return(mod2)
}

# Build plot function for forest plots
build_forest <- function(mod, capt, lsize = 22, ttl = NULL) {
  if(class(mod)[1] == "rma.mv") {
    mod2 <- broom_mod(mod)
  } else {
  # Build dataset for plot
  mod2 <- tibble(
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    bind_rows(.,
              aux = tibble(
                TE = c(mod$TE.random, NA),
                seTE = c(mod$seTE.random, NA),
                studlab = c("Overall Effect",
                            "Prediction Interval"),
                lower = c(mod$lower.random,
                          mod$lower.predict),
                upper = c(mod$upper.random,
                          mod$upper.predict),
                group = "B")) %>%
    group_by(studlab) %>%
    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
    ungroup()
  }

@@

In this paper, we use a multi-level random effects model. The difference between a simple random effects model, and a multi-level random effects model is that we can specify multiple levels of empirical dependency in the data (). The empirical papers testing the *law of 1/n* are very diverse. We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:

@@

In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in [Doing Meta-Analysis with R](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html). To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$. We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it the most precise when analysing continuous measures, such as we have in our data (@veroniki2016methods).

@@

```{r, warning=F, cache=TRUE, echo = FALSE}
## Plot 1
pdf('../graphs/graph1.pdf', width = 16, height = 11)
ggarrange(f1,f3,f5,f4,f6,f2,f7, align = 'hv')
dev.off()
## Plot 2
pdf('../graphs/graph2.pdf', width = 12, height = 6)
ggarrange(f8, f9, align = 'hv')
dev.off()
```
